Inter-task effects lead to an unexpected bias in human computation

### 2014-06-06 docs/publications/2014.05_PNAS/manuscript.tex
rename pnas3.tex -> manuscript.tex

\title{The effects of priming in human computation}
\author{Edward Newel, Derek Ruths}

@@

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun and remuneration \cite{kazai2013analysis}.  Tasks 
involving qualitative
judgment (e.g. flagging inappropriate images), natural language annotation,
and object recognition are commonplace, since people still outperform  
computers in these areas \cite{yuen2011survey}.

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requester can interact with the platform like a compute server, 
seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.

Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and provide qualitative annotations of datasets in a research 
setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
low-commitment engagement with the requester, researchers have criticized the
reliability of crowdsourced output \cite{marsden2009crowdsourcing}.

For one, cheating
is a problem \cite{lease2011quality}, but straightforward methods have been 
developed to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
Still, there is a great deal of variance in worker attention and 
accuracy \cite{kazai2013analysis}.  Researchers have found many factors that 
modulate worker performance, such as level of pay\cite{kazai2013analysis}, 
training\cite{le2010ensuring}, pre-screening 
workers\cite{paolacci2010running}, and user-interface design
\cite{Finnerty2013}.

Here we are concerned with effects of a more subtle origin: the influence that
prior tasks have on subsequent ones.  Psychology experiments document the 
strong effects that a prior exposure to stimulus can have on participants' 
performance in related tasks, a phenomenon known as \textit{priming}[***].  
Strong 
priming effects have been demonstrated for
perceptual tasks such as the visual recognition of 
objects \cite{BJOP:BJOP1796},
auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
of gender[***] and affect[***]: precisely the kinds of tasks well-serviced by 
microtask platforms \cite{yuen2011survey, snow2008cheap}.

In the direction of priming, researchers have investigated various effects 
due to \textit{framing}, by disclosing to the worker the functional role of
their task in the workflow context \cite{Kinnaird2012281}, 
or describing a meaningful ultimate purpose of the project in which their
task is a part \cite{chandler2013breaking}.
However, psychological experiments show that priming is strongest when 
delivered through the same modality as the task [***].  This leads us to 
investigate how priming that occurs \textit{during} a task influences output
of subsequent similar tasks. We call such effects \textit{in-task priming}.

We investigate the effects of in-task priming for an image-labeling task
on the AMT platform.  Each worker is required to label a \textit{prior set} of
images followed by a \textit{posterior set}, but no distinction is made between
these sets from the perspective of the worker.  The posterior set is
always the same, but workers are randomly assigned one of three prior sets.
We analyze the labels workers attribute to the posterior set to see if it is 
affected by the prior set.  As effects, we consider what aspects of image 
content the workers choose to label (the \textit{label orientation}), and how 
specific the labels are (the \textit{label specificity}), both of which have 
direct consequence on the validity of using human computation to make 
qualitative judgments.

As a point of comparison, we subject some groups of workers to a kind of
framing: we disclose a fictitious, semantically-loaded name for the 
task-requester, chosen to signal an interest in a specific aspect of the 
image content.  One might expect that this would strongly sway the labeling 
of the workers.  We do detect the effects of framing, but, remarkably, we find 
that in-task priming has a much stronger effect on label orientation and 
specificity.

This has major implications for the design of qualitative labeling and 
classification tasks.  Our results show that prior tasks can introduce 
significant bias in subsequent worker labeling.  On the other hand, our 
results suggest that the progression of tasks can also be used to tune 
workers to produce more nuanced output.

In psychology, priming is defined as the effect in which a prior stimulus leads
to faster or more accurate responses in a subsequent task than without the
stimulus, or where the stimulus allows the experimenter to the elicit 
responses from subsequent stimuli that are less intense or noisier [***].
However priming might have many effects other than those traditionally 
measured.  We are interested in studying the effects of priming in a human 
computation, we adopt a more general view of priming as HPU hysteresis.

For this purpose, we present an algorithmic definition of priming that
yields a powerful method for detecting priming without knowing ahead of time 
what effects one is looking for.  We demonstrate that this tool is capable of 
distinguishing the priming treatments in our experiment even when the 
differences are subtle.  We expect such a tool will have wide applications 
outside computer science.

@@

One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  A participant always approaches
a task in \textit{some} state of mind.  This will be influenced by her
exposures prior to the experiment, which cannot be known by the experimenter.  
In our experiment, for example, we include a prior image set that is in some
sense ``neutral'', but it is by no means a control group. The particular 
images used would arguably induce different priming than that induced by 
another set that was, in its own way, ``neutral''.
We avoid this difficulty by defining priming relatively, and speak of one
treatment being \textit{differently primed} from another.

Another factor that we must consider is that the effects of priming will
manifest differently depending on the task that participants perform 
subsequent to priming.  Said differently, two priming treatments that
produce markedly different output for one task might be 
indistinguishable under another task.  Thus, we define priming
in relation to the task.

A final factor to consider is that, individuals who are in the same priming 
treatment will still in general produce different output for a task,
due to the natural variance between people.  Therefore, we define priming in 
relation 
to populations, not individuals.

With these considerations, consider two populations of people 
$\mathcal{J}$ and $\mathcal{K}$, that produce respectively two populations of 
outputs $\mathcal{L}$ and $\mathcal{M}$ during the completion of a task 
$\mathcal{T}$:

\vspace{2mm}
\begin{mydef}
	\upshape
	$\mathcal{J}$ and $\mathcal{K}$ 
	\emph{differ in priming by a degree at least $\theta$},
	if there exists an algorithm $\mathcal{A}$ that takes as input 
	$L \subset \mathcal{L}$ and $M \subset \mathcal{M}$ and the output 
	$o$ of a person $p$ chosen with equal probability from either 
	$\mathcal{J}\setminus J$ or $\mathcal{K}\setminus K$, 
	such that $\mathcal{A}$ determines the set from which $p$ was drawn
	($\mathcal{J}$ or $\mathcal{K}$) with accuracy $\frac{1+\theta}{2}$.  
\end{mydef}

In the language of computer science, $\mathcal{A}$ is a classifier.  Thus,
intuitively, if there exists a classifier that can distinguish two populations,
then they are differently primed.

@@

In practice we do not anticipate serious difficulty in choosing a classifier
and establishing a meaningful value of $\theta$.  One of the simplest 
classifier algorithms, the \textit{Naive Bayes classifier}, performs very 
nearly as well as the most sophisticated classifiers in nearly all 
applications [**].  Therefore, we submit $\theta_\text{NB}$, as determined by 
a Naive Bayes classifier, to be a general-purpose measure of priming 
difference.

\subsection*{Experimental Setup}
We solicited 900 AMT workers to perform an image labeling task.  The workers
were randomly assigned to one of seven treatments shown in 
\textbf{Table 1}.  Workers were first shown brief instructions.
Depending on their treatment, they were then either shown the name of 
a research funder followed by a prior image set, or they were immediately 
shown a prior image set. When shown, the funder name was either
``The Global foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness''.  Finally, workers were 
presented the posterior image set, which was the same for all treatments.

The prior and posterior images sets both consist of five images. Workers had
to provide five labels for each image.  For the posterior image set we chose 
images that contain prepared meals and feature a prominent, identifiable 
culture (see \textbf{Fig. 1}).  We intended that the content of these images 
would elicit labels focusing food or culture (or both).

One of the prior image sets, which we call \textit{ambiguous}, was chosen to
be very similar to the posterior image set, in the sense that it consists of
images of prepared meals.  However, the ambiguous image set was chosen such 
that its cultural features are less prominent and more difficult to identify 
(see \textbf{Fig. 2}).  
The \textit{cultural} prior set features iconic cultural scenes, but no food 
at all (see \textbf{Fig. 3}).  Finally, images from
the \textit{ingredients} prior image set depict separated ingredients, but, 
like the ambiguous set, were chosen to avoid prominent cultural features (see 
\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
details.

\subsection*{Results}
\paragraph{The priming of all treatments was easily detectible.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
the classifier performance in distinguishing between different pairs of 
treatments based on workers' labels for the posterior images, and the corresponding
value for $\theta_\text{NB}$.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  Remarkably, the classifier not only 
distinguishes treatments tending toward different ``orientations'' 
(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
it also distinguishes workers from treatments of the \textit{same} 
orientation with high accuracy 
(e.g. $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$, \textbf{Fig. 5B}).
Clearly the algorithmic definition of priming and its implementation as 
$\theta_\text{NB}$ provides a sensitive means for detecting the presence of
primed populations.

Next we look at the degree to which labels from individual posterior images reveal 
priming.  It would stand to reason that, as workers proceed through 
the posterior images, the effects of priming might be ``washed out''.  
\textbf{Figure 6} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later posterior images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
work, we plan to investigate the dynamics of priming wash-out in greater 
detail.

\paragraph{Priming orients focus.} Having demonstrated differential 
priming, we investigate the \textit{nature} of the priming.  To this
end, we construct an ontology of all the labels attributed to
the posterior images.  The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}. We provide more detail about the construction of the 
ontology in the \textbf{Materials and Methods} section.

The ontology allows us to algorithmically count the number of labels that are
of cultural orientation (\texttt{ganesha}),  food orientation
(\texttt{bread}), or both (\texttt{dim sum}).  We do this by counting the
number of labels having have inbound paths leading from the abstract clasess 
\texttt{culture} and/or \texttt{food}, which are present in the ontology.
\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{7A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of labels 
for different images, probably due to inherent differences in their content.  
For our purpose, we are interested in the systematic differences between 
treatments.

In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images of a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also appeas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 7C}, we plot label compositions for only the first posterior
image.  This reveals that, in labeling the first posterior image, workers in 
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.  
This shows that in-task priming effects can dramatically distort the results 
of human computation tasks.

We next inspect this effect longitudinally, that is, as a function of 
the posterior image.  To do so, we compute the \textit{excess cultural orientation} 
($\Delta_{cult}$) of
$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 8} plots $\Delta_{cult}$ as a function of posterior image, $i$. 
This clearly shows the strong influence on the labels attributed to the first 
posterior image,
but for later images the effect immediately drops below statistically 
significant levels, while remaining always positive.

\paragraph{Priming affects attention to detail.} Using the ontology described
in the previous section, we compare treatments in their degree of specificity.
When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
and \texttt{food} are non-comparable.

@@

where $\mathcal{U}$ and $\mathcal{V}$ are treatments, taken as sets of workers.
See \textbf{Materials and Methods} for statistical analysis of the relative 
specificity of two treatments. 
\textbf{Figure 9} 
exhibits the results.

In panel \textbf{9A}, we see that when we compare each of the treatments to
$\textsc{ambg}$, all treatments in which a non-ambiguous prior image set was 
displayed have \textit{lower} specificity (though not all at $\alpha=0.05$).  
In panels \textbf{9D} and \textbf{9G} we compare the same pairs of treatments, 
but restrict to words of culture- and food-orientation respectively (words
of both orientations are excluded).  These plots show that the relative lack 
of specificity is mainly attributable to food-oriented words.

Likewise, in panels \textbf{9B}, and \textbf{9C}, 
wherever we see significant differences in specificity, it turns out that
these differences appear to mainly be due to differences in food specificity,
as can be seen by comparing to panels \textbf{9E}, \textbf{9F}, \textbf{9H}, 
and \textbf{9I}.  In fact, looking to panels \textbf{9D}, \textbf{9E}, and 
\textbf{9F},
there are no significant differences in cultural specificity to speak of. 
Clearly, food and culture are not on equal footing in the experiment.  Various 
psychological explanations are possible, and we explore these in the 
discussion below.

@@

\paragraph{In-task priming is strong.}  We expected that the funder names 
would overtly signal to workers that the requester was interested in a 
specific aspect of image content.  On the other hand, we did not 
expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
strongly affect how the workers approach the task.  Perhaps the most 
unexpected result of this study is that the prior image set influenced label 
orientation and specificity far more than did framing the task by naming the
funder.

This points to a serious hazard in conducting studies using human computation,
academic or otherwise: even if the requester has 
eliminated surrounding influences to every practical extent, 
\textit{the greatest source of bias might lurk in the task itself}.

Randomized ordering and replication of tasks is one method to abate this.
But the requester could also include an initial set of tasks as a 
``tuning phase''.  During the tuning phase, workers would be primed in a 
controlled way, through exposure to tasks that had been specially picked to
orient worker focus in a useful manner.  Moreover, this phase could double as a
screening phase to select quality workers [***].

>>>>

\title{Inter-task effects lead to an unexpected bias in human computation}
\author{Edward Newell, Derek Ruths}

@@

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis, Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and manually annotate of datasets in a research 
setting \cite{snow2008cheap}.  
Tasks involving qualitative
judgment (e.g. flagging inappropriate images), natural language annotation,
and object recognition are commonplace, since it is difficult to achieve 
comparable performance using only computers \cite{yuen2011survey}.
%Generally the worker is first given some orientation to the task, and then 
%performs the task repeatedly (e.g. label several images, one after 
%the other).

Such platforms render human cognition into a fluid resource: it is available 
on demand in small units, with low transaction 
cost, from anywhere via the 
Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requester can 
interact with the platform like a compute server, seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well known that people 
are subject to priming effects 
\cite{BJOP:BJOP1796, No2007, beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549, sohn2001task}.  
We investigate the effects that the content of earlier tasks has on workers'
outputs in later tasks.  We call such effects 
\textit{inter-task priming}.  Inter-task priming would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

This work supplements the existing research into the factors that affect HPU 
output.  Studies have shown that 
there is a great deal of variance in worker attention and 
accuracy \cite{kazai2013analysis}.
Factors that affect the quality of HPU 
output include level of pay\cite{kazai2013analysis}, 
training\cite{le2010ensuring}, pre-screening 
workers\cite{paolacci2010running}, and user-interface design
\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
by disclosing to the worker the role of
their task in a larger workflow context \cite{Kinnaird2012281}, 
or describing a meaningful ultimate purpose of the project in which their
task is a part \cite{chandler2013breaking}.  However, to our knowledge, no
study has investigated the effects of inter-task priming.

To characterize such effects, we present a novel  
\textit{algorithmic definition of priming}, and a corresponding method for
measuring priming effects using machine learning algorithms.  
Traditional methods for detecting priming are of limited use in characterizing 
HPU hysteresis, because they are task-specific, and assume that priming results
in a specific class of effects.
Our approach can be applied to any task output, and does not rely on a prior 
assumption about the particular effects brought about by priming.  This 
enables the detection of priming even when the nature of the effects is not 
understood.

In the present work we investigate inter-task priming for an image-labeling 
task
on the AMT platform.  Each worker is required to label ten images featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
The final image set is always the same, but we randomly assign one of three 
initial sets, and analyze the effect this assignment has on labels attributed 
to the final set.  We employ our novel method for detecting priming effects, as
well as measuring effects on the content and specificity of attributed labels.

As a point of comparison, we also subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically loaded name for the 
task-requester.  The names are chosen to suggest the requester's interest in a 
specific aspect of the image content.  One might reasonably expect that this 
would orient workers to provide a greater quantity and specificity of labels 
which relate to this ``preferred'' content.

Surprisingly, inter-task effects on label orientation and specificity are 
much stronger than those brought about by framing tasks with a funder name. 
Our results 
show that initial tasks can introduce significant bias in subsequent worker 
labeling.  On the other hand, we find evidence that a well-chosen progression 
of tasks could tune workers to produce labels of greater (or lesser) 
specificity.  This suggests that careful consideration should be given to
the progression of tasks when designing a study using a microtask platform.

Even when we are unable to detect priming in the form of a direct
influence on label orientation or specificity, our novel measurement approach 
clearly detects priming. This demonstrates a remarkable feature of the 
approach, whereby priming effects can be quantified without knowing the nature 
of said effects.

@@

In psychology, the effects of priming are usually measured in terms of a 
change in the  
speed or accuracy of responses in a task, or in the ability to recognize a 
stimulus object (e.g. a spoken word or an image) when the object is noisier, 
fainter, or briefer [***].  Methods are also employed to measure processes
in the brain of the participant, such as by fMRI.  These approaches are 
well-suited to studying the underlying psychological mechanisms at work.

Our purpose is different: we are interested in assessing the ramifications
that priming of HPUs could have on the processes in which they are employed.
This influences the approach we take to measurement in two ways.  First, we 
switch from focusing on the internal mechanisms of HPUs to focusing strictly 
on the HPU outputs.  Second, since we cannot \textit{a priori} know the 
application for which HPUs are being employed, we favor generality in the 
kinds of effects that can be detected.  We would like to measure any effects
that could in principle impact the application.  These considerations motivate
us to define priming effects in terms of algorithmic distinguishability of 
the output.

One difficulty in constructing a definition of priming is that there would 
appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
participant 
always approaches a task in \textit{some} state of mind.  If no priming 
condition is applied, then the participant is simply primed by her
exposures prior to the experiment, which cannot be known by the experimenter.  
While arguments can surely be made that one treatment or another is 
\textit{more} 
``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
Instead, we define priming relatively, and speak of one treatment being 
\textit{differently primed} from another.

A definition of priming must also consider that the effects of priming will
manifest differently depending on the task that participants perform 
subsequent to priming:  two priming treatments that
produce markedly different output for one task might be 
indistinguishable under another task.  Thus, we define priming
with respect to a task.

A final factor to consider is that people will always differ in their initial
knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
priming may not be ``complete'', in the sense that people's experiences before
priming may continue to have residual effects.  Therefore, we define priming 
in relation to populations, which we regard as having stable distributions of
such latent attributes.

To set up the definition, when a population of people $\mathcal{J}$ performs
a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$. We will also write 
$\mathcal{T}(j) = \ell$ to indicate that a single person, $j$, output $\ell$ 
during $\mathcal{T}$.

\vspace{2mm}
\begin{mydef}
	\upshape
	Two mutually exclusive populations of people, $\mathcal{J}$ and 
	$\mathcal{K}$, are uniformly and randomly subsampled from an initial 
	population $\mathcal{P}$, are exposed to (possibly) different priming 
	treatments, and then perform a task $\mathcal{T}$, 
	producing task-outputs $\mathcal{T}(\mathcal{J})$ and 
	$\mathcal{T}(\mathcal{K})$.
	We say that $\mathcal{J}$ and $\mathcal{K}$ 
	\emph{differ in priming by a degree at least $\theta$},
	if there exists an algorithm $\mathcal{A}$ that takes as input 
	$\mathcal{T}(J)$, $\mathcal{T}(K)$, and $\mathcal{T}(p)$,
	where $J \subset \mathcal{J}$, $K \subset \mathcal{K}$, and $p$ is a 
	person chosen with equal probability from either $\mathcal{J}\setminus J$ 
	or $\mathcal{K}\setminus K$, 
	such that $\mathcal{A}$ outputs the set from which $p$ was drawn
	($\mathcal{J}$ or $\mathcal{K}$) with accuracy $\frac{1+\theta}{2}$.  
\end{mydef}

In the language of computer science, $\mathcal{A}$ is a classifier.  Thus,
intuitively, if there exists a classifier that can distinguish populations 
$\mathcal{J}$ and $\mathcal{K}$ based on their outputs, then they are 
differently primed.

@@

Note that this definition admits special cases that are equivalent to the
traditional psychological definitions of priming.  If one can show by an
experiment that 
speed, accuracy, or the like, are statistically different for two priming 
treatments, then said experiment could itself be run as a classifier.

This definition substitutes one choice for another: given a task
and two priming treatments, the experimenter need not choose specific effects
to look for, but must instead choose a classifier.  This choice is inherently
less restrictive.  Many general purpose classifiers exist that perform
well in diverse applications [***].  The Naive Bayes classifier stands out as 
a suitable first test to quantify the effects of priming,
because it is simple to implement and requires no domain-specific tuning of 
parameters [***].  We adopt this classifier in the present work and 
denote the measured differences in priming as $\theta_\text{NB}$ to distinguish
them from the theoretical value, $\theta$.

\subsection*{Experimental Setup}
We solicited 900 AMT workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Workers were first shown brief 
instructions.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.  When shown, 
the funder name was either
``The Global Foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness''.  Next, workers were
shown ten images, one at a time, and were required to label each image with
five descriptive labels.  For the purpose of analysis, we divide the images
into the \textit{initial} and \textit{final} sets, which are respectively the 
first five and last five images shown.  However, from the perspective of the 
worker, there was no 
distinction or interruption between the initial and final sets. 
The initial set was chosen from one of three sets, depending on the 
treatment, while the final set was always the same.

For the final image set we chose 
images that contain prepared meals and feature a prominent, identifiable 
culture (see \textbf{Fig. 1}).  We intended that the content of these images 
would elicit labels focusing food or culture (or both).
One of the initial image sets, which we call \textit{ambiguous}, was chosen to
be very similar to the final image set, in the sense that it consists of
images of prepared meals.  However, the ambiguous image set was chosen such 
that its cultural features are less prominent and more difficult to identify 
(see \textbf{Fig. 2}).  
The \textit{cultural} initial set features iconic cultural scenes, but no food 
at all (see \textbf{Fig. 3}).  Finally, images from
the \textit{ingredients} initial image set depict separated ingredients, but, 
like the ambiguous set, were chosen to avoid prominent cultural features (see 
\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
details.

\subsection*{Results}
\paragraph{Earlier tasks and framing both prime workers.}
We tested for priming effects using our definition proposed in the 
introduction, implemented with a Naive Bayes classifier.  
The classifier distinguished the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(inter-task and framing) were effective (\textbf{Fig. 5}).  Remarkably, the 
classifier not only 
distinguished treatments tending toward ``different orientations'' 
(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$; \textbf{Fig. 5A}), 
it also distinguished treatments that one might expect would have similar
effects.  For example the greatest accuracy was achieved in 
distinguishing $\textsc{ingr}_{img}$ and $\textsc{ingr}_{fund, img}$, both
of which are primed for a focus on food 
(see \textbf{Fig. 5B}).

Next we looked at the degree to which labels from individual final images 
reveal priming.  It would stand to reason that, as workers proceed through 
the final images, the effects of priming might be ``washed out''.  
Indeed, when labels from just one of the images
in the final set were used, $\theta_\text{NB}$ was lower for later images (see
\textbf{Figure 6}).
Understanding the dynamics of priming wash-out in greater detail is an 
important direction for future work.

\paragraph{Earlier tasks orient focus during later tasks.} Having 
demonstrated both inter-task and framing effects, we next
investigated the \textit{nature} of these effects.  To this
end, we constructed an ontology of all the labels attributed to
the final images.   
The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}. We provide more detail about the construction of the 
ontology in the \textbf{Materials and Methods} section.

We counted the number of labels that were of cultural- 
or food-orientation,
based on whether the label had inbound paths from the 
abstract classes \texttt{culture} and/or \texttt{food} in the ontology. Of 
course, food is a central feature of culture, so many labels turned out to be
both culture- and food-oriented in this sense.  Nevertheless, there were many 
food-oriented labels, such as \texttt{bread}, which were culturally highly 
ambiguous, and did not have an inbound path from \texttt{culture} in the 
ontology.  Meanwhile, there were many non-food, culture-oriented labels, such
as \texttt{russian dolls}.

%The ontology often contained 
%alternative labels for food which were culturally more specific, for example 
%\texttt{roti}, which are attributed cultural-orientation in the ontology.  
%This provided a degree of freedom upon which inter-task priming and framing 
%might act.

Taking the labels from all treatments together, we observed significant 
variance in the label composition (fraction of food- and culture-oriented 
labels) between the various 
images in the final set (see \textbf{Fig. 7A}).  This is to be expected, due 
to differences in the content of the images; for our purpose, we are 
interested in the systematic differences between treatments, not between 
images.

We compared the composition of labels between different treatments by
aggregating labels attributed to all the images from the final set within a 
given treatment (see \textbf{Fig. 7B}).  
Treatments that began by labeling the cultural images, 
subsequently attributed significantly more culture-oriented and fewer 
food-oriented labels to the final images, as compared to the other 
treatments ($\alpha=0.05$).  Meanwhile, all of the $\textsc{ingr}_x$ 
treatments produced more food-oriented labels, but we cannot assert a 
systematic effect at a significance of $\alpha = 0.05$.

Although the effect on label composition, brought about by having workers 
initially label cultural images, was statistically significant, the effect 
size was admittedly somewhat small (\textbf{Fig 7B}). Since we observed that 
priming 
difference ``wears off'', we analyzed label composition on a per-image basis.
Indeed, for the first image in the final set, workers from 
$\textsc{cult}_{img,x}$ strongly favored culture- over 
food-oriented labels (\textbf{Fig. 7C}). The effect was strong enough to 
essentially invert the proportions of culture- and food-oriented labels 
relative to all other treatments, which favored food-oriented labels.  
This shows that \textit{inter-task effects can dramatically distort the results
of human computation tasks}.

To exhibit the effect longitudinally, as a function of the number of images
labeled since exposure to the initial set, we computed the 
\textit{excess cultural orientation} 
($\Delta_{cult}$) of
$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.  
Intuitively, this is intended to capture how much 
more culture-oriented the labels from $\textsc{cult}_{img}$ are than those
from $\textsc{ambg}$, for image $i$.

The results from this calculation show the strong influence of the 
initial image set on the labels attributed to the first image in the final set
(see \textbf{Fig. 8}).  However, for later images, the effect immediately 
drops below statistically significant levels, while remaining always positive.

\paragraph{Earlier tasks affect attention to detail during later tasks.} 
Using the ontology described
in the previous section, we compared treatments in their degree of specificity.
When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
and \texttt{food} are non-comparable.

@@

where $\mathcal{U}$ and $\mathcal{V}$ are treatments, formally taken
as sets of workers.

When we compared each of the treatments to \textsc{ambg} in this way, 
all treatments in which a non-ambiguous initial image set was 
displayed have \textit{lower} specificity 
(most, but not all, at $\alpha=0.05$; see \textbf{Fig. 9A}).  To understand
how relative specificity is being attributed, we repeated the calculation of 
specificities relative to \textsc{ambg}, but including only the non-food-, culture-oriented 
labels (see \textbf{Figs. 9D}), and only the non-culture-, food-oriented labels
(see \textbf{Fig. 9G}).  These calculations show that the loss of 
specificity of treatments that initially labeled images other than those from
the ambiguous set, was attributable to specificity of food-oriented labels, 
but not culture-oriented ones.

It might be the case that labels of a certain semantic connection are less 
influenced by inter-task effects with regard to specificity. Alternatively,
there may have simply been too few cultural labels for an effect on specificity
to manifest (see \textbf{Fig. 7}).
The lower number of cultural labels might be due to the fact that people's 
vocabulary for cultural concepts is less diverse than that for food, or that 
culture, being more abstract, is less ``imageable'' \cite{Swaab200299}.

Nevertheless, the dramatic drop in overall specificity relative to 
\textsc{ambg}, induced when workers begin by labelling the culture or 
ingredients images, demonstrates that 
inter-task effects can strongly influence the specificity of task output.
This is likely to be a major quality factor in nearly all HPU-driven studies.

\td{count the number of occurrences of cultural and food-oriented labels, 
	to see if the non-responsiveness of culture had to do with restricted
number of labels}.

@@

\paragraph{Inter-task effects are strong.}  We expected that by showing
workers the funder names ``The Global Foundation for Cultural Recognition'',
and ``The National Foundation for Nutritional Awareness'', workers would 
be strongly influenced, interpreting this as and indication of what content 
is salient (culture or food).
To our surprise, it turned out that changing the initial set of images that
workers labeled had a much stronger influence on label orientation and 
specificity than did framing the task by naming the funder.
This points to a serious hazard in conducting studies using human computation,
academic or otherwise: even if the requester has 
eliminated surrounding influences to every practical extent, 
\textit{the greatest source of bias might lurk in the tasks themselves}.

Replication of tasks with randomized ordering is one way to abate inter-task
effects.  But the requester could also include an initial set of tasks as a 
``tuning phase''.  During the tuning phase, workers would be primed in a 
controlled way, through exposure to tasks that had been specially picked to
orient worker focus in a useful manner.  Moreover, this phase could double as a
screening phase to select quality workers [***].  However, a deeper 
understanding of the persistence of inter-task effects is needed to know if 
this is viable.
